



**Required packages**

```{r,message=TRUE, warning=TRUE}

library(dplyr)
library(ggplot2)
library(tidyr)

```


**Importing Data**



```{r,message=TRUE, warning=TRUE}


data <- read.csv("C:/Users/Saina/Desktop/R Project/deliveries.csv")
matches <- read.csv("C:/Users/Saina/Desktop/R Project/matches.csv")
matches <- matches[,-18]
data$wickets <- as.numeric(ifelse(data$player_dismissed =="" ,"",1))
```



**Data wrangling**

```{r,message=TRUE, warning=TRUE}

teams <- data %>% select(batting_team)%>%
  distinct()

teams <- rename(teams, team = batting_team)  

s_team <- c("KKR","RCB","CSK","KXIP","RR","DD","MI","DC","KTK","PWI","SRH","RPS","GL")
teams <- cbind(teams, s_team)

player_of_match <- matches%>% select(id,player_of_match,season) %>%
  distinct()

player_of_match <- rename(player_of_match, player=player_of_match)

Season <- data.frame(season=c(2008,2009,2010,2011,2012,2013,2014,2015,2016),T_winner=c("Rajasthan Royals","Deccan Chargers","Chennai Super Kings","Chennai Super Kings","Kolkata Knight Riders","Mumbai Indians","Kolkata Knight Riders","Mumbai Indians","Sunrisers Hyderabad"))


matches$city <- as.character(matches$city)
matches$city[matches$city==""] <- "Dubai"
venue_city <- matches %>%
            select(city)%>%
  distinct()

#geocodes <- geocode(as.character(venue_city$city))
#venue_city <- data.frame(venue_city[,1],geocodes)

#venue_city <-rename(venue_city,city=venue_city...1.) 

```


**Run rate is high at the end of 1st innings compared to 2nd innings**

```{r,message=TRUE, warning=TRUE}
runs_o <- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
  group_by(season,inning,over)%>%
  summarize(no=n(),runs =sum(total_runs))%>%
  mutate(avg=runs/no)%>%
  filter(inning!=3,inning!=4)
  


ggplot(runs_o,aes(x=season,y=avg,colour=over,group=over))+
  geom_line(show.legend = TRUE, size =1.25,linetype=1)+
      theme(legend.position="bottom")+
  theme(legend.direction = "horizontal") +
  facet_wrap(~inning)+
  scale_y_continuous(name="average runs per ball")+
    scale_x_discrete(name="season",limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Average runs per ball by over each season and innings")

```


**Most batsmen are dismissed being caught**

```{r,message=TRUE, warning=TRUE}
dismissal <- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
   left_join(teams,by=c("batting_team"="team"))%>%
  filter(dismissal_kind!="")%>%
  group_by(season,dismissal_kind,s_team)%>%
  summarize(wickets =n())
  
 
 
ggplot(dismissal,aes(x=dismissal_kind,y=wickets,colour=as.factor(season),fill=as.factor(season)))+
  geom_bar(position = "stack", show.legend = TRUE, width =.6,stat="identity")+
      theme(legend.position="bottom")+
     coord_flip()+
  theme(legend.direction = "horizontal") +
  scale_y_continuous(name="wickets")+
    scale_x_discrete(name="dismissal kind")+
                     ggtitle("Breakdown of dismissal type")

```


Runs scored by tournament winners in each season. 

```{r,message=TRUE, warning=TRUE}

batting_TW <- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
  semi_join(Season, by=c("season"="season","batting_team"="T_winner"))%>%
  left_join(teams,by=c("batting_team"="team"))%>%
                  group_by(season,batting_team,s_team)%>%
      summarize(runs =sum(total_runs))

ggplot(batting_TW,aes(x=season,y=runs,colour=batting_team,fill=batting_team))+
  geom_bar(position = "stack",  show.legend = FALSE, width = .6,stat="identity")+
  geom_text(aes(label=s_team,hjust=-.25, colour="green"))+
  theme(legend.position="none")+
     coord_flip()+
  scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Total Runs by Tournament winners by season")
  
  
```

 wickets taken by tournament winners in each season. 


```{r,message=TRUE, warning=TRUE}

bowling_TW <- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
  semi_join(Season, by=c("season"="season","bowling_team"="T_winner"))%>%
   left_join(teams,by=c("bowling_team"="team"))%>%
      group_by(season,bowling_team,s_team)%>%
 summarize(wicket =sum(wickets,na.rm=TRUE))

ggplot(bowling_TW,aes(x=season,y=wicket,colour=bowling_team,fill=bowling_team))+
  geom_bar(position = "stack",  show.legend = FALSE, width = .6,stat="identity")+
    geom_text(aes(label=s_team,hjust=-.25, colour="green"))+
  theme(legend.position="none")+
     coord_flip()+
  scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Total wickets by Tournament winners by season")
  
  
```

Highest run scorers in each season

```{r,message=TRUE, warning=TRUE}


bastmen<- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
        group_by(season,batsman)%>%
 summarize(runs =max(sum(batsman_runs,na.rm=TRUE)))%>%
  arrange(season,desc(runs))%>%
  filter(runs==max(runs))

ggplot(bastmen,aes(x=season,y=runs,colour=batsman,fill=batsman))+
  geom_bar(position = "stack",  show.legend = FALSE, width = .6,stat="identity")+
    geom_text(aes(label=batsman,hjust=-.25, colour="green"))+
  theme(legend.position="none")+
     coord_flip()+
  scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Highest run scorers by season")

```

Highest Wicket takers in each season

```{r,message=TRUE, warning=TRUE}

bowler<- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
  filter(dismissal_kind!="run out")%>%
        group_by(season,bowler)%>%
 summarize(wicket =max(sum(wickets,na.rm=TRUE)))%>%
  arrange(season,desc(wicket))%>%
  filter(wicket==max(wicket))

ggplot(bowler,aes(x=season,y=wicket,colour=bowler,fill=bowler))+
  geom_bar(position = "stack",  show.legend = FALSE, width = .6,stat="identity")+
    geom_text(aes(label=bowler,hjust=-.25, colour="green"))+
  theme(legend.position="none")+
     coord_flip()+
  scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Highest wickter takers by season")

```


Players with most player of Match awards in each season

```{r,warning=FALSE,message=FALSE}

MOM_ply <-player_of_match %>%
          group_by(season,player)%>%
        summarize(awards =n())%>%
  filter(awards==max(awards))

MOM_bat<- data%>%
  left_join(matches,by=c("match_id"="id"))%>%
            group_by(season,batsman)%>%
 summarize(runs =sum(batsman_runs,na.rm=TRUE))

MOM_bat <- rename(MOM_bat,player=batsman)
  
MOM_ball<- data%>%
  left_join(matches,by=c("match_id"="id" ))%>%
    filter(dismissal_kind!="run out")%>%
           group_by(season,bowler)%>%
 summarize(wicket =sum(wickets,na.rm=TRUE))
  

MOM_ball <- rename(MOM_ball,player=bowler)
  
MOM_field <-data%>%
  left_join(matches,by=c("match_id"="id" ))%>%
             group_by(season,fielder)%>%
 summarize(catches =sum(wickets,na.rm=TRUE))

MOM_field <- rename(MOM_field,player=fielder)

MOM <- MOM_ply%>%
  left_join(MOM_bat,by=c("player"="player","season"="season"))%>%
  left_join(MOM_ball,by=c("player"="player","season"="season"))%>%
left_join(MOM_field,by=c("player"="player","season"="season"))%>%
group_by(season,player)%>%
 summarize(awards=max(awards),runs=sum(runs,na.rm=TRUE),wickets=sum(wicket,na.rm=TRUE),catches=sum(catches,na.rm=TRUE))


MOM

MOM <- gather(MOM, type, scores,3:6)
type <- MOM$type=="runs"
MOM_r <-MOM[type,]
type_n <- MOM$type !="runs"
MOM_n <- MOM[type_n,]

ggplot(MOM_r,aes(x=season,y=scores,colour=player,fill=player))+
  geom_bar(position = "stack", show.legend = FALSE, width = .6,stat="identity")+
      theme(legend.position="none")+
  geom_text(aes(label=player,hjust=-.25, colour="green"))+
     coord_flip()+
  scale_y_continuous(name="Total Runs")+
  scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Total Runs for Most no of Player of Match awards in a season")


ggplot(MOM_n,aes(x=season,y=scores,colour=type,fill=type))+
  geom_bar(position = "dodge", show.legend = TRUE, width = .6,stat="identity")+
      theme(legend.position="bottom")+
     coord_flip()+
  scale_y_continuous(name="Wickets,catches and NO of awards")+
  scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Most no of Player of Match awards in a season")

```

Total runs scored by each team across all seasons


```{r,message=TRUE, warning=TRUE}

team_runs <- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
    left_join(teams,by=c("batting_team"="team"))%>%
                  group_by(season,batting_team,s_team)%>%
      summarize(runs =sum(total_runs))



ggplot(team_runs,aes(x=season,y=runs,colour=s_team,fill=s_team))+
  geom_line(show.legend = TRUE, size =1.25,linetype=1)+
      theme(legend.position="bottom")+
  theme(legend.direction = "horizontal") +
  scale_y_continuous(limits = c(1500,3000))+
    scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Total runs by teams by season")

```

Total wickets taken by each team across all seasons.  


```{r,message=TRUE, warning=TRUE}

team_wickets <- data%>%
  left_join(matches, by=c("match_id"="id"))%>%
    left_join(teams,by=c("bowling_team"="team"))%>%
                  group_by(season,bowling_team,s_team)%>%
      summarize(wicket =sum(wickets,na.rm=TRUE))



ggplot(team_wickets,aes(x=season,y=wicket,colour=s_team,fill=s_team))+
  geom_line(show.legend = TRUE, size =1.25,linetype=1)+
      theme(legend.position="bottom")+
  theme(legend.direction = "horizontal") +
  scale_y_continuous(limits = c(60,125))+
    scale_x_discrete(name="Season", limits=c(2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  ggtitle("Total wickets by teams by season")

```

Runs scored by each team in 1s, 2s, 3s, 4s,and 6s.

```{r,message=TRUE, warning=TRUE}
runs_cat <- data %>%
  left_join(matches,by=c("match_id"="id"))%>%
   left_join(teams,by=c("batting_team"="team"))%>%
  group_by(s_team,batsman_runs)%>%
  summarize(no=n(),runs=sum(total_runs))

runs_cat$batsman_runs <- as.factor(runs_cat$batsman_runs)
 
ggplot(runs_cat,aes(x=s_team,y=runs,colour=batsman_runs,fill=batsman_runs))+
  geom_bar(position = "stack", show.legend = TRUE, width =.6,stat="identity")+
      theme(legend.position="bottom")+
  theme(legend.direction = "horizontal") +
  scale_y_continuous(name="Runs")+
    scale_x_discrete(name="Teams")+
                     ggtitle("Total runs scored in 1s to 6s")

```

Strike rate of all batsman

```{r,message=TRUE, warning=TRUE}

Bat_sr<- data %>%
  left_join(matches,by=c("match_id"="id"))%>%
   left_join(teams,by=c("batting_team"="team"))%>%
  group_by(batsman)%>%
  summarize(balls=n(),runs=sum(batsman_runs))%>%
  mutate(sr=runs*100/balls)%>%
  arrange(desc(sr))%>%
  mutate(sr_grp=ifelse(sr<100,"100",ifelse(sr<150,"100-150","150+")))%>%
  mutate(player_lab=ifelse(batsman=="AD Russell","AD Russell",ifelse(batsman=="V Sehwag","V Sehwag",ifelse(batsman=="V Kohli","V Kohli",ifelse(batsman=="CH Gayle","CH Gayle","")))))
 


ggplot(Bat_sr,aes(x=sr,y=runs,colour=sr_grp,fill=sr_grp,size=runs))+
  geom_jitter(show.legend = TRUE,alpha=.75)+
      theme(legend.position="bottom")+
    theme(legend.direction = "horizontal") +
    geom_text(aes(label=player_lab,hjust=-.25, colour="red"))+
  scale_y_continuous(name="Runs")+
    scale_x_continuous(name="strike rate")+
                     ggtitle("strike rate for batsman   ")
```

Strike rate  and Economy rate for all bowlers

```{r,message=TRUE, warning=TRUE}


ball_sr<- data %>%
  left_join(matches,by=c("match_id"="id"))%>%
   left_join(teams,by=c("bowling_team"="team"))%>%
    group_by(bowler)%>%
  summarize(balls=n(),runs=sum(total_runs,na.rm=TRUE))

ball_wk <-data %>%
  left_join(matches,by=c("match_id"="id"))%>%
   left_join(teams,by=c("bowling_team"="team"))%>%
  filter(dismissal_kind!="run out")%>%
    group_by(bowler)%>%
  summarize(wickets=sum(wickets,na.rm=TRUE))

ball_sr <-ball_sr%>%
  left_join(ball_wk,by=c("bowler"="bowler"))%>%
  mutate(sr=runs/wickets)%>%
  mutate(er=runs/(balls/6))%>%
    arrange(desc(sr))%>%
  mutate(sr_grp=ifelse(sr<10,"10",ifelse(sr<40,"11-40","41+")))%>%
  mutate(er_grp=ifelse(er<6,"6",ifelse(er<10,"6-10","11+")))%>%
  mutate(player_l=ifelse(bowler=="SL Malinga","SL Malinga",ifelse(bowler=="DJ Bravo","DJ Bravo",ifelse(bowler=="R Ashwin","R Ashwin",ifelse(bowler=="DW Steyn","DW Steyn","")))))
  
 


ggplot(ball_sr,aes(x=sr,y=wickets,colour=sr_grp,fill=sr_grp,size=wickets))+
  geom_jitter(show.legend = TRUE,alpha=.75)+
      theme(legend.position="bottom")+
    theme(legend.direction = "horizontal") +
    geom_text(aes(label=player_l,hjust=-.25, colour="red"))+
  scale_y_continuous(name="Wickets")+
    scale_x_continuous(name="strike rate ")+
                     ggtitle("strike rate for bowlers  ")



ggplot(ball_sr,aes(x=er,y=runs,colour=er_grp,fill=er_grp,size=runs))+
  geom_jitter(show.legend = TRUE,alpha=.75)+
      theme(legend.position="bottom")+
    theme(legend.direction = "horizontal") +
    geom_text(aes(label=player_l,hjust=-.25, colour="red"))+
  scale_y_continuous(name="Runs")+
    scale_x_continuous(name="Economy rate ")+
                     ggtitle("Economy rate for bowlers  ")
```

Number of Toss and Match wins by each team

```{r,message=TRUE, warning=TRUE}
toss <- matches%>%
  left_join(teams,by=c("toss_winner"="team") )%>%
  select(s_team,toss_winner)%>%
   group_by(s_team)%>%
      summarize(wins=n())

toss$type <- "toss"
 
wins <-matches%>%
  left_join(teams,by=c("winner"="team") )%>%
  select(s_team,winner)%>%
   group_by(s_team)%>%
      summarize(wins=n())

wins$type <- "wins"

toss_w <- rbind(toss,wins)

toss_w <- toss_w %>%
  group_by(s_team, type)%>%
summarize(wins=sum(wins))


ggplot(toss_w,aes(x=s_team,y=wins,colour=type,fill=type))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="right")+
       scale_y_continuous(name="Toss and Match Wins")+
  scale_x_discrete(name="Toss and Match winner")+
  ggtitle("Toss and Match wins by each Team")


```

Toss decisions of toss winners

```{r,message=TRUE, warning=TRUE}
wins_1 <- matches%>%
  left_join(teams,by=c("toss_winner"="team") )%>%
  select(s_team,toss_winner,toss_decision)%>%
   group_by(s_team,toss_decision)%>%
      summarize(wins=n())


ggplot(wins_1,aes(x=s_team,y=wins,colour=toss_decision,fill=toss_decision))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="right")+
       scale_y_continuous(name="Toss decision")+
  scale_x_discrete(name="Toss winners and toss decisions")+
  ggtitle("Toss decisions by each Team")

```

All Cities with Average runs, Average wickets per match and matches played.

```{r,message=TRUE, warning=TRUE}
 

venue_c <- data%>%
  left_join(matches,by=c("match_id"="id"))%>%
   select(match_id,city,total_runs,wickets)%>%
  group_by(city)%>%
  summarize(runs=sum(total_runs),wickets=sum(wickets,na.rm=TRUE))

city_mat <- matches %>%
  group_by(city)%>%
  summarize(matches=n())
 
venue_c <- venue_c %>%
  left_join(city_mat, by=c("city"="city"))%>%
  mutate(Avg_runs=runs/matches)%>%
  mutate(Avg_wkt =wickets/matches)%>%
  arrange(city)
  
venue_all <- venue_c%>%
  left_join(venue_city, by=c("city"="city"))%>%
  arrange(Avg_runs)
 
 venue_all$city <- factor(venue_all$city, levels = venue_all$city[order(venue_all$Avg_runs)])
 
ggplot(venue_all,aes(x=city,y=Avg_runs,colour=city,fill=city))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="none")+
  coord_flip()+
       scale_y_continuous(name="Average runs per match")+
   scale_x_discrete(name="Cities ")+
   ggtitle("Average score per match  at each city")


 venue_all$city <- factor(venue_all$city, levels = venue_all$city[order(venue_all$Avg_wkt)])
 
ggplot(venue_all,aes(x=city,y=Avg_wkt,colour=city,fill=city))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="none")+
  coord_flip()+
       scale_y_continuous(name="Average wickets per match")+
  scale_x_discrete(name="Cities ")+
  ggtitle("Average wickets per match at each city")



 venue_all$city <- factor(venue_all$city, levels = venue_all$city[order(venue_all$matches)])
 
ggplot(venue_all,aes(x=city,y=matches,colour=city,fill=city))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="none")+
  coord_flip()+
       scale_y_continuous(name="Total no of Matches in each city")+
  scale_x_discrete(name="Cities ")+
  ggtitle("Cities with most no of matches")


```

Matches with highest winning margins by runs and wickets 

```{r,message=TRUE, warning=TRUE}

win_r <- matches%>%
 left_join(teams,by=c("winner"="team"))%>%
  select(s_team,id,winner,win_by_runs,win_by_wickets)%>%
  arrange(desc(win_by_runs),desc(win_by_wickets))%>%
  filter(!is.na(s_team))

win_w <-win_r[,-4]
win_r <- win_r[,-5]

win_w <- win_w %>%arrange(desc(win_by_wickets))%>%
  filter(win_by_wickets>8)
win_r <- win_r %>%arrange(desc(win_by_runs))%>%
  filter(win_by_runs>60)

win_w$win_by_wickets <-as.numeric(win_w$win_by_wickets)
win_r$win_by_runs <-as.numeric(win_r$win_by_runs)


win_r$id <- factor(win_r$id, levels = win_r$id[order(win_r$win_by_runs)])
 
ggplot(win_r,aes(x=id,y=win_by_runs,colour=s_team,fill=s_team))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="none")+
  coord_flip()+
  geom_text(aes(label=s_team,hjust=-.25, colour="green"))+
       scale_y_continuous(name="winning margins by runs")+
  scale_x_discrete(name="Match ID's ")+
  ggtitle("Highest winning margins by runs")


 win_w$id <- factor(win_w$id, levels = win_w$id[order(win_w$win_by_wickets)])
 
ggplot(win_w,aes(x=id,y=win_by_wickets,colour=s_team,fill=s_team))+
  geom_bar(position = "dodge",stat = "identity")+
        theme(legend.position="none")+
  coord_flip()+
  geom_text(aes(label=s_team,hjust=-.25, colour="green"))+
       scale_y_continuous(name="winning margins by wickets")+
  scale_x_discrete(name="Match ID's")+
  ggtitle("Highest winning margins by wickets")

```

Highest runs scorers across all seasons.

```{r,message=TRUE, warning=TRUE}

runs_h <- data%>%
        left_join(matches,by=c("match_id"="id"))%>%
  left_join(teams,by=c("batting_team"="team"))%>%
select(batsman,season,s_team,batsman_runs)%>%
group_by(batsman,season,s_team)%>%
summarize(runs=sum(batsman_runs))%>%
arrange(desc(batsman))


run_gh<-runs_h%>%
  group_by(batsman)%>%
  summarize(runs_t=sum(runs))

runs_ht <- merge(runs_h,run_gh)
runs_ht <- runs_ht%>%
  arrange(desc(runs_t))%>%
  filter(runs_t>2500)
  
  
runs_ht$season<-as.character(runs_ht$season)
runs_ht$batsman <- factor(runs_ht$batsman, levels = run_gh$batsman[order(run_gh$runs_t)])


  ggplot(runs_ht,aes(x=batsman,y=runs,colour=season,fill=season))+
  geom_bar(position = "stack",stat = "identity")+
        theme(legend.position="bottom")+
  coord_flip()+
        scale_y_continuous(name="Total runs scored across all seasons")+
  scale_x_discrete(name="Players")+
  ggtitle("Highest run scorers across all seasons")



```

Highest wicket takers across all seasons.

```{r,message=FALSE,warning=FALSE}

wickets_h <- data%>%
        left_join(matches,by=c("match_id"="id"))%>%
  left_join(teams,by=c("bowling_team"="team"))%>%
  filter(dismissal_kind!="run out")%>%
select(bowler,season,s_team,wickets)%>%
group_by(bowler,season,s_team)%>%
summarize(wickets=sum(wickets,na.rm=TRUE))%>%
arrange(desc(bowler))


wickets_gh<-wickets_h%>%
    group_by(bowler)%>%
  summarize(wickets_t=sum(wickets))

wickets_ht <- merge(wickets_h,wickets_gh)
wickets_ht <- wickets_ht%>%
  arrange(desc(wickets_t))%>%
  filter(wickets_t>75)
  
  
wickets_ht$season<-as.character(wickets_ht$season)
wickets_ht$bowler <- factor(wickets_ht$bowler, levels = wickets_gh$bowler[order(wickets_gh$wickets_t)])


  ggplot(wickets_ht,aes(x=bowler,y=wickets,colour=season,fill=season))+
  geom_bar(position = "stack",stat = "identity")+
        theme(legend.position="bottom")+
  coord_flip()+
        scale_y_continuous(name="Total wickets across all seasons")+
  scale_x_discrete(name="Bowlers")+
  ggtitle("Highest wicket takers across all seasons")


```

Players with most number of catches and run outs.

```{r}
catches_h <- data%>%
        left_join(matches,by=c("match_id"="id"))%>%
  left_join(teams,by=c("bowling_team"="team"))%>%
  filter(fielder!="")%>%
  select(fielder,season,s_team,wickets)%>%
group_by(fielder,season,s_team)%>%
summarize(catches=sum(wickets,na.rm=TRUE))%>%
arrange(desc(fielder))


catches_gh <-catches_h%>%
    group_by(fielder)%>%
  summarize(catches_t=sum(catches))


catches_ht <- merge(catches_h,catches_gh)
catches_ht <- catches_ht%>%
  arrange(desc(catches_t))%>%
  filter(catches_t>45)
  
  
catches_ht$season<-as.character(catches_ht$season)
catches_ht$fielder <- factor(catches_ht$fielder, levels = catches_gh$fielder[order(catches_gh$catches_t)])


  ggplot(catches_ht,aes(x=fielder,y=catches,colour=season,fill=season))+
  geom_bar(position = "stack",stat = "identity")+
        theme(legend.position="bottom")+
  coord_flip()+
        scale_y_continuous(name="Total catches & run outs across all seasons")+
  scale_x_discrete(name="fielders")+
  ggtitle("Highest catches and run outs across all seasons")

```

Players scoring most number of runs between 50 and 99 in a inning.

```{r,warning=FALSE,message=FALSE}

fifties_h <- data%>%
        left_join(matches,by=c("match_id"="id"))%>%
  left_join(teams,by=c("batting_team"="team"))%>%
    select(match_id,batsman,season,s_team,batsman_runs)%>%
group_by(match_id,batsman,season,s_team)%>%
summarize(runs=sum(batsman_runs,na.rm=TRUE))%>%
  mutate(fifties=ifelse(runs<50,"49",ifelse(runs<100,"50+","100+")))%>%
  group_by(batsman,season,s_team,fifties)%>%
  summarize(no=n(),runs=sum(runs))%>%
arrange(desc(batsman))%>%
  filter(fifties!=49)


fifties_gh <-fifties_h%>%
      filter(fifties!="100+")%>%
    group_by(batsman)%>%
  summarize(fifties_t=sum(no))


fifties_ht <- merge(fifties_h,fifties_gh)
fifties_ht <- fifties_ht%>%
  filter(fifties!="100+")%>%
  arrange(desc(fifties_t))%>%
  filter(fifties_t>15)
  
  
fifties_ht$season<-as.character(fifties_ht$season)
fifties_ht$batsman <- factor(fifties_ht$batsman, levels = fifties_gh$batsman[order(fifties_gh$fifties_t)])


  ggplot(fifties_ht,aes(x=batsman,y=no,colour=season,fill=season))+
  geom_bar(position = "stack",stat = "identity")+
        theme(legend.position="bottom")+
  coord_flip()+
        scale_y_continuous(name="No of Fifties in a inning across all seasons")+
  scale_x_discrete(name="Batsman")+
  ggtitle("Batsman with highest no of Fifties across all seasons")

```

Players scoring most number of runs above 100 in a inning.

```{r}

century_gh <-fifties_h%>%
      filter(fifties!="50+")%>%
    group_by(batsman)%>%
  summarize(centuries_t=sum(no))



centuries_ht <- merge(fifties_h,century_gh)
centuries_ht <- centuries_ht%>%
  filter(fifties!="50+")%>%
  arrange(desc(centuries_t))
  
  
  
centuries_ht$season<-as.character(centuries_ht$season)
centuries_ht$batsman <- factor(centuries_ht$batsman, levels = century_gh$batsman[order(century_gh$centuries_t)])


  ggplot(centuries_ht,aes(x=batsman,y=no,colour=season,fill=season))+
  geom_bar(position = "stack",stat = "identity")+
        theme(legend.position="bottom")+
  coord_flip()+
        scale_y_continuous(name="No of centuries in a inning across all seasons")+
  scale_x_discrete(name="Batsman")+
  ggtitle("Batsman with highest no of centuries across all seasons")

```


